Minimax-optimal Laplacian Eigenmaps regression over Sobolev Spaces with Neighborhood Graphs

### 2021-10-29 manuscripts/laplacian_eigenmaps/appendix.tex
Responded to all of Siva's comments.

>>>>

\section{Notation Table}
\label{sec:notation_table}

\begin{table}[h]
	\begin{center}
		\begin{tabular}{p{.14\textwidth} | p{.5\textwidth} }
			Symbol & Definition
			\\
			\hline
			$\mc{X}$ & domain, either an open set in $\Rd$ (Model~\ref{def:model_flat_euclidean}) or a compact manifold embedded in $\Rd$ (Model~\ref{def:model_manifold}) \\
			$\nu$ & Lebesgue measure \\
			$\mu$ & volume form induced by the embedding of $\mc{X}$ into $\Rd$ \\
			$P$ & probability measure associated with the design points \\
			$p$ & density of the probability measure, either with respect to $\nu$ (Model~\ref{def:model_flat_euclidean}) or $\mu$ (Model~\ref{def:model_manifold}). \\
			$L^2(\mc{X})$ & set of square-integrable functions, meaning either $\int_{\mc{X}} f^2 \,d\nu < \infty$ (Model~\ref{def:model_flat_euclidean}) or $\int_{\mc{X}} f^2 \,d\mu < \infty$ (Model~\ref{def:model_manifold}). \\
			$C^k(\mc{X})$ & functions which are $k$-times continuously differentiable in $\mc{X}$ \\
			$C_c^{\infty}(\mc{X})$ & functions in $C^{\infty}(\mc{X})$ which are compactly supported in $\mc{X}$ \\
			$H^s(\mc{X})$ & order-s Sobolev space (Definition~\ref{def:sobolev_space} under Model~\ref{def:model_flat_euclidean}, Definition~\ref{def:sobolev_space_manifold} under Model~\ref{def:model_manifold}.) \\
			$H_0^s(\mc{X})$ & order-s zero-trace Sobolev space (Definition~\ref{def:zero_trace_sobolev_space}) \\
			$\|\cdot\|_2$ & Euclidean distance \\
			$d_{\mc{X}}(\cdot,\cdot)$ & geodesic distance \\
			$B(x,\delta)$ & Ball in Euclidean distance, centered at $x$ with radius $\delta$ \\
			$B_{\mc{X}}(x,\delta)$ & Ball in geodesic distance
		\end{tabular}
	\end{center}
	\caption{Notation.}
\end{table}

### 2021-10-29 manuscripts/laplacian_eigenmaps/arxiv/laplacian_eigenmaps_regression.tex
Responded to all of Siva's comments.

% Abstract
\begin{abstract}
	In this paper we study the statistical properties of Principal Components Regression with Laplacian Eigenmaps (PCR-LE), a method for nonparametric regression based on Laplacian Eigenmaps (LE). PCR-LE works by projecting a vector of observed responses ${\bf Y} = (Y_1,\ldots,Y_n)$ onto a subspace spanned by certain eigenvectors of a neighborhood graph Laplacian. We show that PCR-LE achieves minimax rates of convergence over continuum function classes. Specifically, we consider the problem of random design regression over Sobolev spaces $H^s(\mc{X})$---where $\mc{X} \subseteq \Rd$ is the support of the design distribution $P$---and show that under sufficient smoothness conditions on the design density $p$, PCR-LE achieves the optimal rates for both estimation (where the optimal rate in squared $L^2$ norm is known to be $n^{-2s/(2s + d)}$) and goodness-of-fit testing ($n^{-4s/(4s + d)}$). We also show that PCR-LE is \emph{manifold adaptive}: that is, we consider the situation where $\mc{X}$ is a manifold of small intrinsic dimension $m$, and give upper bounds establishing that PCR-LE achieves the faster minimax estimation ($n^{-2s/(2s + m)}$) and testing ($n^{-4s/(4s + m)}$) rates of convergence. Interestingly, these rates are almost always much faster than the known rates of convergence of graph Laplacian eigenvectors to their population-level limits; in other words, for this problem regression with learned features appears to be much easier, statistically speaking, than feature learning itself. We support these theoretical results with empirical evidence.
\end{abstract}

@@

>>>>

% Abstract
\begin{abstract}
	In this paper we study the statistical properties of Principal Components Regression with Laplacian Eigenmaps (PCR-LE), a method for nonparametric regression based on Laplacian Eigenmaps (LE). PCR-LE works by projecting a vector of observed responses ${\bf Y} = (Y_1,\ldots,Y_n)$ onto a subspace spanned by certain eigenvectors of a neighborhood graph Laplacian. We show that PCR-LE achieves minimax rates of convergence for random design regression over Sobolev spaces. Under sufficient smoothness conditions on the design density $p$, PCR-LE achieves the optimal rates for both estimation (where the optimal rate in squared $L^2$ norm is known to be $n^{-2s/(2s + d)}$) and goodness-of-fit testing ($n^{-4s/(4s + d)}$). We also show that PCR-LE is \emph{manifold adaptive}: that is, we consider the situation where $\mc{X}$ is a manifold of small intrinsic dimension $m$, and give upper bounds establishing that PCR-LE achieves the faster minimax estimation ($n^{-2s/(2s + m)}$) and testing ($n^{-4s/(4s + m)}$) rates of convergence. Interestingly, these rates are almost always much faster than the known rates of convergence of graph Laplacian eigenvectors to their population-level limits; in other words, for this problem regression with estimated features appears to be much easier, statistically speaking, than estimating the features itself. We support these theoretical results with empirical evidence.
\end{abstract}

@@

\newpage
